---
title: "Extracting Pokemon data using R scripts"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extracting Pokemon data using R scripts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteDepends{dplyr,pogor,DT}
  \usepackage[utf8]{inputenc}
---


The data are supplied in a data frame, `pkmn`, with one row per currently-released Pokémon. This is a decoded version of the GAME_MASTER file included in the game package, with a few columns added on the end. 

```{r}
library(DT)
library(pogor)
datatable(pkmn, extensions='FixedColumns', options=list(fixedColumns=list(leftColumns=2), scrollX = TRUE))
```

We can use tools from the `dplyr` package to explore and extract subsets of the data in a "tidy" way.

```{r, message=FALSE, warning=FALSE}
library(dplyr)
```

For example, explore the chances that each Pokémon will attack at a certain point during the catch encounter.  Slakoth is among the lowest, as might be expected from the idle creature.

```{r, warning=FALSE}
pkmn %>% select(pokemonId, encounter.attackProbability) %>% arrange(encounter.attackProbability) %>% head
```

But what about the highest?  I knew Tyranitar was pretty aggressive.  But I was surprised to see it was Vigoroth, the first evolution of Slakoth. I look forward to encountering one of these in the wild!

```{r}
pkmn %>% select(pokemonId, encounter.attackProbability) %>% arrange(desc(encounter.attackProbability)) %>% head
```

There are ten variables in this data file that appear to govern how Pokémon behave during the encounter.  [The Silph Road](https://thesilphroad.com/science/wild-pokemon-encounter-mechanics/) have studied some of these in detail. 

```{r}
#[15] "encounter.movementType"              
#[16] "encounter.movementTimerS"            
#[17] "encounter.jumpTimeS"                 
#[18] "encounter.attackTimerS"              
#[19] "encounter.attackProbability"         
#[20] "encounter.dodgeProbability"          
#[21] "encounter.dodgeDurationS"            
#[22] "encounter.dodgeDistance"             
#[24] "encounter.minPokemonActionFrequencyS"
#[25] "encounter.maxPokemonActionFrequencyS"
```

What about the lowest base capture rates? 

```{r}
pkmn %>% select(pokemonId, encounter.baseCaptureRate) %>% arrange(encounter.baseCaptureRate) %>% head(20)
```

Or the highest base capture rates? 
```{r}
pkmn %>% select(pokemonId, encounter.baseCaptureRate) %>% 
  filter(!is.na(encounter.baseCaptureRate)) %>% arrange(desc(encounter.baseCaptureRate)) %>% head(20)
```

Find the base capture rate for a particular Pokémon.  Surprised Slakoth isn't higher - I'll be surprised the first time I see it jumping out of a Pokéball.
```{r}
pkmn %>% filter(pokemonId == "SLAKOTH") %>% select(encounter.baseCaptureRate) # 0.4
```

Fury Cutter is a great fast move.  Which Pokémon can learn it? 
```{r}
pkmn %>% filter(quickMoves.V1 == "FURY_CUTTER_FAST" | quickMoves.V2 == "FURY_CUTTER_FAST") %>% select(pokemonId)
```
