

# 8 variables for animation time? 


# Collision height against collision radius
```{r}
p <- ggplot(pkmn, aes(x=encounter.collisionRadiusM, y=encounter.collisionHeightM, text=pokemonId)) + 
  geom_point(aes(col=type)) + type_ggcols
ggplotly(p)
```

# Collision head radius (?) against collision radius
```{r}
p <- ggplot(pkmn, aes(x=encounter.collisionRadiusM, y=encounter.collisionHeadRadiusM, text=pokemonId)) + 
  geom_point(aes(col=type)) + type_ggcols
ggplotly(p)
```

# Collision radius against camera distance
```{r}
p <- ggplot(pkmn, aes(x=encounter.collisionRadiusM, y=encounter.cameraDistance, text=pokemonId)) + 
  geom_point(aes(col=type)) + type_ggcols
ggplotly(p)
```

why does eevee have a bigger collision radius than sentret?  Camera distances are very similar

Variables determining Pokemon activity while catching (see recent silph road analysis (?) explaining these)

[15] "encounter.movementType"              
[16] "encounter.movementTimerS"            
[17] "encounter.jumpTimeS"                 
[18] "encounter.attackTimerS"              
[19] "encounter.attackProbability"         
[20] "encounter.dodgeProbability"          
[21] "encounter.dodgeDurationS"            
[22] "encounter.dodgeDistance"             
[24] "encounter.minPokemonActionFrequencyS"
[25] "encounter.maxPokemonActionFrequencyS"


# height and weight with SD TODO